Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2021-04-21 Thesis/article.tex
thesis powersession

\documentclass[a4paper]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	colorlinks = false,
	linkbordercolor = {white},
	urlcolor = {blue},
	linkcolor = {blue},
	citecolor = {blue}
}
\usepackage{acronym}
\usepackage[acronym,nomain]{glossaries}
\makeglossaries
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\me}[1]{\textbf{\textcolor{gray}{#1}}}
\newcommand{\ds}[1]{}
\newcommand{\oc}{$^o$C}

@@

%\clearpage
\printglossaries
%\clearpage
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preface}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\td{describe everything what is meantioned in \ref{sec:exp}}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Aims and Objectives}
was hab ich gemacht, warum? 
Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
sich selbst aufnehmen

Präsentieren: Visualisierungen sinnvoll? 
Antworten überlegen/Argumente überlegen
Limitation, Rahmen der Arbeit
Begründung für die eigene Vorgehensweise
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
\section{Experimental}
\label{sec:exp}
In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (2.5~cm~x~7.5~cm) \td{from where}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from where}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from where}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) \td{provided by Sunplugged GmbH (\url{http://sunplugged.at/)}}.
The glass slides and \gls{fto} were cut\td{/scratched} with a \td{diamond scratcher/scraper} and broken with a \td{glass breaker} into pieces of dimensions 2.5~cm~x~2.5~cm.
The steel foil was cut with a foil cutter\me{, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting slides)}.
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
	\item 15 minutes in \gls{water} in a sonic bath
	\item 15 minutes in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Cutting of the steel foil}
\label{sec:cut}
There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
Alternatively, the foil can be cut without bending by cutting repeatedly with a cutter knife.
The foil is cut into 2.5 x 2.7 mm plates.
The small plates are marked with an diamond cutter pen.
The plates are cleaned with 1ml of Hellmanex III in 50-100 ml \gls{water} in the sonic bath for 15 min, then in \gls{water} for 15 min and finally in \gls{ipo} for 15 min. 
The samples are dry blown with dry N$_2$ and stored until doctor blading.
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solution}
Two main recipes were used and their \td{ingredients/compositions} were varied. 
The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
and the second recipe - 
adopted from Hu et. al. \cite{Hu2016} -
was based on \gls{zrpro} in \gls{buoh}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aquatic solution}
\me{The procedure for the aquatic solution is as follows:}
While stirring \gls{zrpro} is added to \gls{acac} and \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) is added to \gls{ipo} in two separate vessels and stirred for 1 hour. 
The \gls{water}-\gls{ipo} mixture is added to the other solution and stirred over night. 
The exact volumes can be taken from table \ref{tab:rec1}.
\begin{table}[h]
	\centering
	\caption{}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
%		\hline
%		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
		\hline
		\gls{zrpro} [ml]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac} [ml]		&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo} [ml]		&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [ml]		&2.6	&2.6	&2.5	&2		&2		&2		&2\\
		\gls{sds} [mg]		&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl} [ml]		&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [ml]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh} [ml] 	&-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Buthanolic solution}
\label{sec:sol}
\td{make recipe general}
%The recipe for the solution was adapted from ref \cite{Hu2016}.
Five different concentration were prepared. 
%The first solution \td{(standard concentration/ one fold/ 1F)} 
%followed the recipe loosely, which is described by Hu et al. \cite{Hu2016}.
%In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
The \gls{1f} \td{(one fold (1F) solution /or/ one fold solution (1F))}
%one-fold concentrated solution (1F) 
was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
%
%was closely on the basis of ref \cite{Hu2016}. 
%The standard concentration will be described first and then the differences of higher concentrated solutions:
4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with \td{an air-tight} cap) with a stirrer. 
0.1 ml of \gls{zrpro} are added while stirring.  
After 10 to 15 minutes 0.05 ml (\ds{approximately }one mole equivalent of \gls{zrpro}) chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
In order to make a 
%double concentrated 
\gls{2f}
solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
The real concentration is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.

@@

@@

scarce data may lead to overfitting\cite{Lecun1995conv}
\section{Results and Discussion}
The space seems to be too big for the small sample size.
Look at relation of space size and sample size here and in Hu2016.
\section{Outlook}

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\hypersetup{
	colorlinks = true,
	colorlinks = false,
	linkbordercolor = {white},
	urlcolor = {blue},
	linkcolor = {blue},
	citecolor = {blue}
}
\usepackage{acronym}
\usepackage[acronym,nomain]{glossaries}
\makeglossaries
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\me}[1]{\textbf{\textcolor{gray}{#1}}}
\newcommand{\ds}[1]{}
\newcommand{\oc}{$^o$C}

@@

\clearpage
\printglossaries
%\clearpage
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preface}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\td{describe everything what is meantioned in \ref{sec:exp}}
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Aims and Objectives}
was hab ich gemacht, warum? 
Defensio: Argumente in der Arbeit noch mal sichten, Feedback von Betreuungsperson im Kopf haben - da könnten Fragen kommen, 
sich selbst aufnehmen

Präsentieren: Visualisierungen sinnvoll? 
Antworten überlegen/Argumente überlegen
Limitation, Rahmen der Arbeit
Begründung für die eigene Vorgehensweise
%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL
\section{Theoretical Background aka How does is work?}
\subsection{Sputtering}
\subsection{SEM}
\subsection{Infrared absorbance}

\section{Experimental}
\label{sec:exp}
In this section the used chemicals and substrates, experimental procedures and any used equipment are described. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (2.5~cm~x~7.5~cm) \td{from Sigma Aldrich}, thinner, squared glass plates (2.5~cm~x~2.5~cm) \td{from Sigma Aldrich}, \gls{ito} glass plates (2.5~cm~x 2.5~cm) \td{from Sigma Aldrich}, \gls{fto} glass plates (5~cm~x~5~cm) from \td{Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
The glass slides and \gls{fto} were \ds{cut\td{/scratched}}scratched with a scratching tool \ds{\td{(diamond scratcher/scraper)} }and broken with a \td{glass breaker} into pieces with dimensions 2.5~cm~x~2.5~cm.
The steel foil was cut with a foil cutter, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item 15 minutes in 50 ml \gls{water} and 1 ml of Hellmanex III in a sonic bath
	\item 15 minutes in \gls{water} in a sonic bath
	\item 15 minutes in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were dry blown with dry \gls{n2} gas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Cutting of the steel foil}
\label{sec:cut}
There is a red foil cutter in the vacuum room, which cuts the foil without much bending.
Alternatively, the foil can be cut without bending by cutting repeatedly with a cutter knife.
The foil is cut into 2.5 x 2.7 mm plates.
The small plates are marked with an diamond cutter pen.
The plates are cleaned with 1ml of Hellmanex III in 50-100 ml \gls{water} in the sonic bath for 15 min, then in \gls{water} for 15 min and finally in \gls{ipo} for 15 min. 
The samples are dry blown with dry N$_2$ and stored until doctor blading.
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solution}
Two main recipes were used and their compositions were varied. 
The first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} 
and the second recipe - 
adopted from Hu et. al. \cite{Hu2016} -
was based on \gls{zrpro} in \gls{buoh}.

%\iffalse
\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		%\includegraphics[width=.99\textwidth]{Pics/sol-aq.png}
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		%\includegraphics[width=.99\textwidth]{Pics/sol-bu.png}
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution in beaker glass sealed with Parafilm}
\end{figure}
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aquatic solution}
\me{The procedure for the aquatic solution is as follows:}
\gls{zrpro} was added to \gls{acac} while stirring and in a seperate vessel \gls{water} (including any additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) was added to \gls{ipo} and both were stirred for 1 hour. 
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table \ref{tab:rec1}.
\begin{table}[h]
	\centering
	\caption{}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
%		\hline
%		conc. [a.u.]	&1		&1.7	&2.6	&3.5	&4.4	\\
		\hline
		\gls{zrpro} [ml]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac} [ml]		&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo} [ml]		&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [ml]		&2.6	&2.6	&2.5	&2		&2		&2		&2\\
		\gls{sds} [mg]		&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl} [ml]		&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [ml]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh} [ml] 	&-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Buthanolic solution}
\label{sec:sol}
Five different concentration were prepared. 
%The first solution \td{(standard concentration/ one fold/ 1F)} 
%followed the recipe loosely, which is described by Hu et al. \cite{Hu2016}.
%In order to obtain thicker \gls{zro} layers the \gls{zrpro} concentration in the starting solution was raised.
The \gls{1f} 
was closest to the recipe proposed by Hu et. al. \cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f}, \gls{5f}) were similar with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
The procedure for obtaining the \gls{1f} solution will be explained in detail: \td{maybe just keep it general}
%
%was closely on the basis of ref \cite{Hu2016}. 
%The standard concentration will be described first and then the differences of higher concentrated solutions:
4.9 ml of solvent (\gls{buoh}) are put into a beaker glass (or similar, preferably with an air-tight cap) with a stirrer. 
0.1 ml of \gls{zrpro} are added while stirring.  
After 10 to 15 minutes 0.05 ml (\ds{approximately }one mole equivalent of \gls{zrpro}) chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
Finally, 1 ml of stabilisation solvent (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The solvent (\gls{buoh}) is put into a beaker glass (or similar, preferably with an air-tight cap) with a stirrer and \gls{zrpro} is added while stirring.  
After stirring 10 to 15 minutes one mole equivalent chelating agent (\gls{acac}) is added and stirred for another 10 to 15 minutes. 
Finally, the stabilisation solvent\cite{Hu2016} (\gls{ipo} or \gls{acoh}) is added to the mixture and stirred for additional 20-30 minutes. 
Following stirring times (in minutes) were tested and didn't have an influence on stability of the solution: 10-10-20, 10-10-45, 30-30-180. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In order to make a \gls{2f} solution, the volume of \gls{zrpro} and \gls{acac} is doubled and \gls{buoh} is decreased by the volume of \gls{zrpro}. 
The real concentration of a \gls{2f} solution is not double of the original, though, but rather 1.7 fold because volume of \gls{ipo} is kept constant.

@@

\subsection{Characterisation}
\subsubsection{SEM}
Zeiss Supra 40
\subsubsection{Infrared}
Bruker Vertex 70
\subsubsection{X-Ray Defraction}
Thermo Scientific ARL Equinox 100 X-Ray Diffractometer
\subsubsection{Current-Voltage Curve}
Agilent 4156C Precision Semiconductor Parameter Analyzer
\begin{figure}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{Pics/i-v.png}
		\label{fig:iv-agilent}
		\caption{peripherals}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{Pics/i-v-micro.png}
		\label{fig:iv-micro}
		\caption{View through the microscope}
	\end{subfigure}
	\label{fig:iv}
	\caption{I-V curve abnehm aperature and sicht durch das micro scope.}
\end{figure}

@@

scarce data may lead to overfitting\cite{Lecun1995conv}
\section{Results and Discussion}
The space seems to be too big for the small sample size.
Look at relation of space size and sample size here and in Hu2016.

Would be easier to fit with single factor at a time variation or latin hyper cuber?
Would it also be easier for PSO or ML to find fitting function?
Every output var is independent of each other, so $v_{cal}$ can act as test

\section{Outlook}
